\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-28 jss/article.tex
edit
double space
minor 8schools edits

%%uncomment line below for double-spacing
%%\linespread{2}

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
This output from \code{gbp} summarizes the results. In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$. As such schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$. The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit because every school's $95\%$ posterior interval contains 0.

@@

And simple unbiased coverage estimates and their standard errors for each player are
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
[13] 0.957 0.969 0.972 0.982 0.978 0.984
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
\end{CodeOutput}
\end{CodeChunk}

>>>>

%%uncomment line below for double-spacing
\linespread{2}

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
This output from \code{gbp} summarizes the results. In this Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_j = V_j/(V_j + A)$. As such, schools whose variation within the school ($V_{j}$) is less than the between variation ($A$) schools will shrink greater than $50\%$. The results provided by \code{gpb} suggests that there is little evidence that the training provided much added benefit due to the fact that every school's $95\%$ posterior interval contains 0.

@@

And simple unbiased coverage estimates and their standard errors for each player are
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.969 0.967 0.973 0.980 0.970 0.974 0.965 0.976 0.969 0.972 0.980 0.972 
[13] 0.957 0.969 0.972 0.982 0.978 0.984
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0045 0.0059 0.0066 0.0049 0.0052 0.0044 0.0042 0.0054 0.0056 0.0053 0.0049 
[11] 0.0056 0.0042 0.0049 0.0056 0.0057 0.0052 0.0052
\end{CodeOutput}
\end{CodeChunk}
